---
title: "p8105_hw1_qz2266"
author: "Qing Zhou"
date: "2022-09-23"
output: github_document
---

```{r setup}
library(tidyverse)
```

# Problem 1

## Descriptive summaries of the penguins dataset

```{r penguins}
data("penguins", package = "palmerpenguins")

ncol(penguins)
colnames(penguins)
nrow(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)

class(pull(penguins, species))
nlevels(pull(penguins, species))
levels(pull(penguins, species))

class(pull(penguins, bill_length_mm))
mean(pull(penguins, bill_length_mm), na.rm = TRUE)
median(pull(penguins, bill_length_mm), na.rm = TRUE)
range(pull(penguins, bill_length_mm), na.rm = TRUE)
```

The penguins data set has `r ncol(penguins)` variables, including `r colnames(penguins)`.  There are `r nrow(penguins)` observations in total in this data set. 

The mean flipper length (mm) is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` after excluding two NAs.

Other important variables include species, which is a `r class(pull(penguins, species))` variable and consists of `r nlevels(pull(penguins, species))` levels including `r levels(pull(penguins, species))`, and bill length, which is a `r class(pull(penguins, bill_length_mm))` variable, with the mean value of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm, and the median value of `r median(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. Moreover, the range of values for the penguin bill length is 
(`r  range(pull(penguins, bill_length_mm), na.rm = TRUE)` mm).


## Make a scatterplot and export the plot

```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Penguin Flipper Length vs. Bill Length by Species")

ggsave("scatterplot_penguin.pdf", height = 4, width = 6)
```



# Problem 2

## Create a data frame
```{r create_df}
prob2_df = 
  tibble(
    var_numeric = rnorm(10),
    var_logic = var_numeric > 10,
    var_char = c("My", "name", "is", "Vivian", "Zhou", "and", "I", "love", "data", "science"),
    var_factor = factor(c("mild", "mild", "mild", "moderate", "moderate", "moderate", "moderate","severe", "severe", "severe"))
  )
prob2_df
```




