---
title: "p8105_hw1_qz2266"
author: "Qing Zhou"
date: "2022-09-23"
output: github_document
---

```{r setup}
library(tidyverse)
```

# Problem 1

## Descriptive summaries of the penguins dataset

```{r penguins}
data("penguins", package = "palmerpenguins")

ncol(penguins)
colnames(penguins)
nrow(penguins)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)

class(pull(penguins, species))
nlevels(pull(penguins, species))
levels(pull(penguins, species))

class(pull(penguins, bill_length_mm))
mean(pull(penguins, bill_length_mm), na.rm = TRUE)
median(pull(penguins, bill_length_mm), na.rm = TRUE)
range(pull(penguins, bill_length_mm), na.rm = TRUE)
```

The penguins data set has `r ncol(penguins)` variables, including `r colnames(penguins)`.  There are `r nrow(penguins)` observations in total in this data set. 

The mean flipper length (mm) is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` after excluding two NAs.

Other important variables include species, which is a `r class(pull(penguins, species))` variable and consists of `r nlevels(pull(penguins, species))` levels including `r levels(pull(penguins, species))`, and bill length, which is a `r class(pull(penguins, bill_length_mm))` variable, with the mean value of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm, and the median value of `r median(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. Moreover, the range of values for the penguin bill length is 
(`r  range(pull(penguins, bill_length_mm), na.rm = TRUE)` mm).